---
title: "socialbladeR: A Package Scraping the website Social Blade"
author: "Maxwell Skinner"
date: '2023-05-11'
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# socialbladeR

<!-- badges: start -->
<!-- badges: end -->

The goal of socialbladeR is to get 

## Installation

You can install the development version of socialbladeR like so:

```{r}
library(remotes)
remotes::install_github("maxwellskinner2002/socialbladeR")
library(socialbladeR)
```

## Example

This is a basic example which of using the function yt_topcategories, which will return a dataframe of the top 50 subscribed accounts by that specific category.

```{r example}
yt_topcategories("autos")
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
